Appendix 2: Manuscript and Exploratory Code

### 2025-06-16 manuscript_code.Rmd
tidying including additional metrics

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
library(worcs)
library(tidyverse)
library(gtsummary)
library(likert)
library(here)
library(corrplot)
library(ggstats)
library(lavaan)
library(lavaanPlot)
library(kableExtra)
library(naniar)

library(gridExtra)
#library(semPlot) # update plots to semPlot later
#library(blavaan) # could not get it to work with this model and synthetic data, try as sensitivity analysis later
#library(tidySEM) # https://github.com/yrosseel/lavaan/issues/359 lavaan does not work if tidySEM is loaded!
# renv::status() to check 
# renv::snapshot() to add used and install to renv

@@

```
```

@@

library(psych)
corrplot(cor(data.fit.miss,use="pairwise.complete.obs"), method ='number')

@@

@@

###  b) Sum score model with bootstrapping and listwise deletion

@@

#end of exploratory analysis
knitr::knit_exit()

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
library(worcs)
library(tidyverse)
library(gtsummary)
library(likert)
library(here)
library(corrplot)
library(ggstats)
library(lavaan)
library(lavaanPlot)
library(kableExtra)

#additional packages added (plotting, cronbach's alpha)
library(naniar)
library(psych)
library(gridExtra)

#library(semPlot) # update plots to semPlot later
#library(blavaan) # could not get it to work with this model and synthetic data, try as sensitivity analysis later
#library(tidySEM) # https://github.com/yrosseel/lavaan/issues/359 lavaan does not work if tidySEM is loaded!
# renv::status() to check 
# renv::snapshot() to add used and install to renv

@@

@@

corrplot(cor(data.fit.miss,use="pairwise.complete.obs"), method ='number')

@@

## Cronbach's Alpha

scalepo <- data.fit2 %>% select(starts_with("po"))
scaleid <- data.fit2 %>% select(starts_with("si"))
scaleint <- data.fit2 %>% select(starts_with("it"))
scaleco <- data.fit2 %>% select(starts_with("ac"))
scalekn <- data.fit2 %>% select(starts_with("ai"))
scaleiv <- data.fit2 %>% select(starts_with("iv"))

alpha(scalepo)
alpha(scaleid)
alpha(scaleint)
alpha(scaleco)
alpha(scalekn)
alpha(scaleiv)

@@

#  b) Sum score model with bootstrapping and listwise deletion

@@
